Learning Constraints and Optimization Criteria

### 2015-10-23 Paper.tex
Title caps & more formal optimization experiments

\paragraph{Learning constraints}
Constraint learning attempts to automatically identify constraints in one or multiple examples.
This task is hard because the search space of constraints is typically very large and, unlike in typical machine learning problems, there are usually only few examples to learn from.

@@

\subsection{Constraint learning}
\emph{Given a set of examples and a limit $t$, the goal is to find maximally specific clauses that are satisfied by at least $t$ of the given examples.}
\\\\
Examples are Herbrand interpretations.
They consist of set of constants, the domain, and all ground atoms over these constants that are true.
The learned clauses are domain-independent and contain only variables.

\subsection{Learning optimization criteria}
\emph{Given a set of examples \sym{E} and a set of preferences \sym{P} over these examples, the goal is to learn soft constraints and weights such that the order described by these optimization criteria maximally corresponds with~\sym{P}.}
\\\\
Every preference $p \in \sym{P}$ describes a relative order $e_1 \succ e_2 \succ ... \succ e_n$ over a subset of examples $\{e_1, e_2, ..., e_n\} \subseteq \sym{E}$.
A preference $e_1 \succ e_2$ indicates that out of examples $e_1$ and $e_2$ the user prefers $e_1$.

@@

\begin{question}[Compared to humans]
  How do learned constraints compare to human programmed constraints?
\end{question}
Human programmed theories for map coloring and sudoku are available on the website of the IDP system \footnote{https://dtai.cs.kuleuven.be/software/idp}.
These theories usually focus on being compact and contain only the essential constraints.
Table~\ref{tbl:mens} shows the results of two experiments that measure the time to find a solution for a new problem.
This time is measured for the learned theories as well as for hand made theories.
The learned theories are slightly adapted to be able to solve the same problems and remove unfair advantages such as preprocessed input data.

@@

Preferences are generated by picking two examples $e_1$,~$e_2 \in \sym{E}_{train}$ and ordering them according to their score: $score(e_i, \sym{M})$.
Consider all possible pairwise preferences over $\sym{E}_{train}$: $\mathit{pref}(\sym{E}_{train})$.
Given the fraction $p_{pref}$ of preferences to use, then a random subset~$\sym{P}_{train} \subset \mathit{pref}(\sym{E}_{train})$ of size $p_{pref} \cdot \# \sym{P}$ is used for learning.
Errors in the input preferences are simulated by flipping preferences (e.g. $e_1 \succ e_2$ becomes $e_1 \prec e_2$).
Given the fraction $p_{error}$ of errors to introduce, a random subset $\sym{P}_{error} \cup \sym{P}_{train}$ of the preferences are flipped, where $\#\sym{P}_{error} = p_{error} \cdot \sym{P}_{train}$.

@@

Figure~\ref{fig:fractie} shows how the scores improve as the number of examples and the fraction of included preferences increases.
In all cases, more than half the pairs of examples are correctly predicted and high scores can be obtained even for small datasets.
Additional experiments have shown that even for lower scores the learned optimization criteria are often capable of identifying the correct optimal solution. \sam{Refer to thesis}

@@

\begin{question}[Noise]
  What is the influence of noise on the accuracy?
\end{question}

The influence of noise is shown in figure~\ref{fig:ruis}.
Hereby, the second approach of testing is applied, using potentially overlapping train- and test sets.
High scores are obtained, even despite significant levels of noise.
The figure also shows that providing more rankings improves the robustness of the algorithm, even if the relative amount of noise remains unchanged.

@@

  \begin{table}[!htp]
    \caption{Scores for different thresholds ($t$)}
    \begin{tabularx}{\linewidth}{XXXX}
      $t = 1$ & $t = 2$ & $t = 3$ & $t = 4$ \\
      \toprule
     0.823 & 0.740 & 0.788 & 0.735 \\
     ($\pm$ 0.073)&
($\pm$ 0.078)&
($\pm$ 0.074)&
($\pm$ 0.063)
    \end{tabularx}
    \label{tbl:limiet}
  \end{table}

@@

Table~\ref{tbl:limiet} demonstrates that increasing the threshold used for finding soft constraints does not improve the score.
This experiment used 40\% of the examples as training set and 40\% of the available rankings.
However, if the size of the problem and examples is increased, a higher threshold will likely be appropriate.

@@

The constraint learning implementation has been able to learn the relevant hard and soft constraints in all experiments.
For each problem, only a small number of examples was given to learn from.
The system requires only a minimal amount of information from the user, however, it also allows for the use of expressive background knowledge.
The learned constraints are domain independent \sam{review domain}, which facilitates the construction of positive examples.

>>>>

\paragraph{Learning Constraints}
The goal of constraint learning is to automatically identify constraints in one or multiple examples.
This task is difficult because the search space of constraints is typically very large and, unlike in typical machine learning problems, there are usually only few examples to learn from.

@@

\subsection{Constraint Learning}
\emph{Given a set of examples and a limit $t$, the goal is to find maximally specific clauses that are satisfied by at least $t$ of the given examples.}
\\\\
Examples are Herbrand interpretations.
They consist of set of constants, the domain, and all ground atoms over these constants that are true.
The learned clauses are domain-independent and contain only variables.

\subsection{Learning Optimization Criteria}
\emph{Given a set of examples \sym{E} and a set of preferences \sym{P} over these examples, the goal is to learn soft constraints and weights such that the order described by these optimization criteria maximally corresponds with~\sym{P}.}
\\\\
Every preference $p \in \sym{P}$ describes a relative order $e_1 \succ e_2 \succ ... \succ e_n$ over a subset of examples $\{e_1, e_2, ..., e_n\} \subseteq \sym{E}$.
A preference $e_1 \succ e_2$ indicates that out of examples $e_1$ and $e_2$ the user prefers $e_1$.

@@

\begin{question}[Compared to humans]
  How do learned constraints compare to human programmed constraints?
\end{question}
Human programmed theories for map coloring and sudoku are available on the website of the IDP solver\footnote{https://dtai.cs.kuleuven.be/software/idp}.
These theories usually focus on being compact and contain only the essential constraints.
Table~\ref{tbl:mens} shows the results of two experiments that measure the time to find a solution for a new problem.
This time is measured for the learned theories as well as for hand made theories.
The learned theories are slightly adapted to be able to solve the same problems and remove unfair advantages such as preprocessed input data.

@@

Preferences are generated by picking two examples $e_1$,~$e_2 \in \sym{E}_{train}$ and ordering them according to their score: $score(e_i, \sym{M})$.
Consider all possible pairwise preferences over $\sym{E}_{train}$: $\mathit{pref}(\sym{E}_{train})$.
If the fraction of preferences to be used is~$p_{pref}$, then a random subset~$\sym{P}_{train} \subset \mathit{pref}(\sym{E}_{train})$ of size $p_{pref} \cdot \# \sym{P}$ is used for learning.
Errors in the input preferences are simulated by flipping preferences (e.g. $e_1 \succ e_2$ becomes $e_1 \prec e_2$).
Given the fraction $p_{error}$ of errors to introduce, a random subset $\sym{P}_{error} \cup \sym{P}_{train}$ of the preferences are flipped, where $\#\sym{P}_{error} = p_{error} \cdot \sym{P}_{train}$.

@@

\sam{change figures}
Figure~\ref{fig:fractie} shows how the scores improve as the fractions of examples ($p_{train}$) and preferences ($p_{pref}$) that are used for learning increase.
In all cases, more than half the pairs of examples are correctly predicted and high scores can be obtained even for small datasets.
Additional experiments have shown that even for lower scores the learned optimization criteria are often capable of identifying the correct optimal solution. \sam{Refer to thesis}

@@

\begin{question}[Errors]
  What is the influence of errors in preferences on the accuracy?
\end{question}

The influence of errors is shown in figure~\ref{fig:ruis}.
Hereby, the second approach of testing is applied using overlapping train- and test sets.
High scores are obtained, even despite significant levels of noise.
The figure also shows that increasing the number of preferences used for learning ($p_{pref}$) improves the robustness of the algorithm, even if the relative amount of errors ($p_{error}$) remains unchanged.

@@

  \begin{table}[!htp]
    \caption{Accuracy for different thresholds ($t$)}
    \begin{tabularx}{\linewidth}{XXXX}
      $t = 1$ & $t = 2$ & $t = 3$ & $t = 4$ \\
      \toprule
     0.823 & 0.740 & 0.788 & 0.735 \\
     ($\pm$ 0.073)&
($\pm$ 0.078)&
($\pm$ 0.074)&
($\pm$ 0.063)
    \end{tabularx}
    \label{tbl:limiet}
  \end{table}

@@

Table~\ref{tbl:limiet} demonstrates that increasing the threshold used for finding soft constraints does not improve the accuracy ($p_{train} = p_{pref} = 0.4$).
However, if the number of examples is increased, a higher threshold will likely be appropriate.

@@

The constraint learning implementation has been able to learn the relevant hard and soft constraints in all experiments.
For each problem, only a small number of examples was given to learn from.
The system requires only a minimal amount of information from the user, however, it also allows for the use of expressive background knowledge.
Constraints that are learned from examples do not depend on the domains used in those examples.
This 
The learned constraints are independent of the domains used in the examples, which facilitates the construction of positive examples.
